Flowchart of Current Algorithm

### 2008-10-26 docs/flowchart/flowchart.tex
add use_tfromp

Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature
\begin{equation}
T^{(2),\star} = T\left(\rho^{(2),\star}, h^{(2),\star}, X_k^{(2),\star}\right) {\hbox{ \rm using the equation of state.}}
\end{equation}

@@

%--------------------------------------------------------------------------
% STEP 8.1
%--------------------------------------------------------------------------
\item Diffuse the enthalpy through a time interval of $\dt$.  Compute $\kth^{(2),\star}, c_p^{(2),\star}$, and $\xi_k^{(2),\star}$, from $\rho^{(2),\star}, T^{(2),\star}$, and $X_k^{(2),\star}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla h^{(2)} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2)}$,
\begin{eqnarray}
\left(\rho^{(2)} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla\right)h^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature
\begin{equation}
T^{(2)} = T\left(\rho^{(2)}, h^{(2)}, X_k^{(2)}\right) {\hbox{ \rm using the equation of state.}}
\end{equation}

>>>>

Compute $\kth^{(1)}, c_p^{(1)}$, and $\xi_k^{(1)}$ from $\rho^{(1)}, T^{(1)}$, and $X_k^{(1)}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(2),\star} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2),\star}$,
\begin{eqnarray}
\left(\rho^{(2),\star} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla\right)h^{(2),\star} &=& (\rho h)^{(2'),\star} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(2),\star} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(2),\star} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature using the equation of state.

The default is to do
\begin{equation}
T^{(2),\star} = T\left(\rho^{(2),\star}, h^{(2),\star}, X_k^{(2),\star}\right) \enskip ,
\end{equation}
but if {\tt use\_tfromp = T}, then we do
\begin{equation}
T^{(2),\star} = T\left(\rho^{(2),\star}, p_0^{(2),\star}, X_k^{(2),\star}\right) \enskip .
\end{equation}
This has the effect of completely decoupling the enthalpy equation from the 
evolution.

@@

%--------------------------------------------------------------------------
% STEP 8.1
%--------------------------------------------------------------------------
\item Diffuse the enthalpy through a time interval of $\dt$.  Compute $\kth^{(2),\star}, c_p^{(2),\star}$, and $\xi_k^{(2),\star}$, from $\rho^{(2),\star}, T^{(2),\star}$, and $X_k^{(2),\star}$ as inputs to the equation of state.  The update is given by
\begin{eqnarray}
(\rho h)^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\left(\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla h^{(2)} + \frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
which is numerically implemented as a diffusion equation for $h^{(2)}$,
\begin{eqnarray}
\left(\rho^{(2)} - \frac{\dt}{2}\nabla\cdot\frac{\kth^{(2),\star}}{c_p^{(2),\star}}\nabla\right)h^{(2)} &=& (\rho h)^{(2')} + \frac{\dt}{2}\nabla\cdot\frac{\kth^{(1)}}{c_p^{(1)}}\nabla h^{(1)}\nonumber\\
&&- \frac{\dt}{2}\sum_k\nabla\cdot\left(\frac{\xi_k^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla X_k^{(2)} + \frac{\xi_k^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla X_k^{(1)}\right)\nonumber\\
&&- \frac{\dt}{2}\nabla\cdot\left(\frac{h_p^{(2),\star}\kth^{(2),\star}}{c_p^{(2),\star}}\nabla p_0^{(2)} + \frac{h_p^{(1)}\kth^{(1)}}{c_p^{(1)}}\nabla p_0^{(1)}\right),
\end{eqnarray}
\item Update the temperature using the equation of state

The default is to do
\begin{equation}
T^{(2)} = T\left(\rho^{(2)}, h^{(2)}, X_k^{(2)}\right) \enskip ,
\end{equation}
but if {\tt use\_tfromp = T}, then we do
\begin{equation}
T^{(2)} = T\left(\rho^{(2)}, {p_0}^{(2)}, X_k^{(2)}\right) \enskip .
\end{equation}
This has the effect of completely decoupling the enthalpy equation from the 
evolution.
